% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins

\name{Sujeethan Vigneswaran}
\address{  sujeethan.vigneswaran@gmail.com  \\ www.sujeethanvigneswaran.com }

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Associate Product Manager}{January 2021 - April 2021}{Loblaw Digital}{Remote}
\item Revamped PC Optimum Insiders subscription flow and homepage design and implementation on iOS, Web and Android to increase acquisition and meet a key performance indicator of 250,000 active users. 
\item Facilitated decision making on program promotions by creating customer journey maps and ensuring cross functional communication in engineering, design, QA, product and marketing teams. 
\item Prioritized features for development using a data-driven methodology by analysing user experience testing results and querying a 15 petabyte database to identify customer insights.
\item  Ensured timely delivery of MVP by breaking down complex technical tasks into 50 detailed user stories and coordinating bi-weekly sprint retrospectives, backlog grooming, and sprint planning.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Site Reliability Engineer}{May 2020 - August 2020}{Loblaw Digital}{Remote}
\item Designed and launched enterprise product and methodology to automate productivity platform licensing on Slack, Jira, GitLab, and PagerDuty. This initiative resulted in a savings of 15 hours per week of toil and \$10,000 per month in licensing fees. 
\item Leveraged quantitative analysis knowledge to publish two dashboard to monitor multi-tenant compute cluster usage providing actionable cost reducing insights.
\item Migrated logging, alerting and metrics from Splunk to Stackdriver on all production services across the enterprise resulting in savings of over \$1 million in 2020.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Big Data Developer}{September 2019 - January 2020}{DRVN Intelligence}{Toronto, ON}
\item Facilitated product road-map development for a three product suite of SaaS tools in programmatic advertising automation that projected revenue of \$25,000 per month.
\item Orchestrated the technical development of a healthcare data engineering solution in a request for proposal for Trillium Health Partners.
\item Pioneered the organization wide adoption of the infrastructure as code methodology using Terraform to manage public cloud infrastructure. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Marketing Intelligence Automation Engineer}{January 2019 - April 2019}{Loblaw Digital}{Toronto, ON}
\item Conducted quantitative analysis on petabytes of transaction logs to forecast success of PC Express locations.
\item Automated microservice and ETL based digital marketing processes  to reduce toil by 11 hours per week.
\item Designed and implemented A/B Tests to use the least PII and mobile device identifiers (IDFA \& GAID) to increase customer segmentation match rates on Adobe Audience Manager by 30\%. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf University of Waterloo, Faculty of Engineering} \hfill { Expected April 2023} \\ 
B.ASc. in Environmental Engineering Option in Management Sciences \\
Relevant Courses: Technical Communication, Digital Computation, Statistics, Economics

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATION SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Certifications}

% {\bf Google Cloud Professional Cloud Architect} \hfill {\em Expires: November 2021} \\ 
% Enables organizations to leverage the cloud with thorough understanding of cloud architecture, and can design, develop, and manage solutions to drive business objectives.

% {\bf Google Cloud Professional Data Engineer} \hfill {\em Expires: December 2021} \\ 
% Enables data-driven decision making by collecting, transforming and publishing data, and can design, build, operationalize, and monitor data processing systems.

% \end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Product & User Stories, Usability Testing, GTM Strategy, Figma, Miro \\
Technology & Python, SQL, Golang, Docker, Kubernetes, Google Cloud Platform \\
Analytics & Google Analytics, Adobe Analytics, Tableau  \\

\end{tabular}

\end{rSection}

\end{document}

